Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-27 methods-and-results.Rmd
:sparkles: variables

@@

\subsubsection{Variables}
We focus on ...

full methodological details are available in Online Supplemental Material A, but basic item information, descriptives, and correlations are available in \tblref{tab:??}

>>>>

```{r variables included in main analysis by response type, include=FALSE}
varNames %>%
  filter(
    pca != 0,
    varNam %in% c(varNamS123PCA, varNamS1PCA, varNamS2PCA, varNamS3PCA)
  ) %>%
  mutate(
    contactSpecific = recode(
      .$contactSpecific,
      `-1` = "No Interaction Only",
      `0` = "unspecific",
      `1` = "Interaction Only"
    ),
    study1 = ifelse(!is.na(studyS1), 1, 0),
    study2 = ifelse(!is.na(studyS2), 1, 0),
    study3 = ifelse(!is.na(studyS3), 1, 0)
  ) %>% 
  select(varNam, varGroup, contactSpecific, study1, study2, study3) %>%
  filter(study1 == 1 & study2 == 1 & study3 == 1) %>%
  group_by(varGroup, varNam, contactSpecific, study1, study2, study3) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = c("varGroup", "varNam", "study1", "study2", "study3"), values_from = n, names_sep=" - ") %>%
  ungroup %>%
  t %>%
  as.data.frame %>%
  janitor::row_to_names(1) %>%
  replace(is.na(.), 0) %>%
  tibble::rownames_to_column(., var = "variable") %>%
  separate(variable, c("concept", "variable", "study1", "study2", "study3"), " - ") %>%
  mutate(across(c(study1, study2, study3), as.numeric)) %>%
  arrange(concept, unspecific, `Interaction Only`) %>% 
  mutate_all(~recode(.x, `0`="", ` 1`="✓")) %>%
  relocate(starts_with("study"), .after = last_col()) %>%
  rename_with(., ~ gsub("study", "Study ", .x, fixed = TRUE)) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "l", rep("c", ncol(.)-2)),
      digits=2,
      caption = "Variables by Interaction Types and Study Availability") %>%
  add_header_above(c(" " = 2, "Contact Type" = 2, "Study Availability" = 3)) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

@@

\subsubsection{Variables}
Included 12 variables that were available across all three studies and captured information about the participant's interactions, as well as cognitive-, emotional-, and motivational self in relationship with the majority group. We chose these two aspects in particular because (1) the interaction-specific information exemplified the structural missingness issue of modern ESM data and (2) the motivational, cognitive, and emotional experience offered a diverse conceptualization of migration experience (beyond behavioral measurements) that is becoming more common in the literature \citep[][]{Kreienkamp2022d}. Full methodological details are available in Online Supplemental Material A, but basic item information, descriptives, and correlations are available in \tblref{tab:??}.

### 2022-11-27 methods-and-results.tex
:sparkles: variables

We focus on \ldots{}

full methodological details are available in Online Supplemental
Material A, but basic item information, descriptives, and correlations
are available in \tblref{tab:??}

>>>>

Included 12 variables that were available across all three studies and
captured information about the participant's interactions, as well as
cognitive-, emotional-, and motivational self in relationship with the
majority group. We chose these two aspects in particular because (1) the
interaction-specific information exemplified the structural missingness
issue of modern ESM data and (2) the motivational, cognitive, and
emotional experience offered a diverse conceptualization of migration
experience (beyond behavioral measurements) that is becoming more common
in the literature \citep[][]{Kreienkamp2022d}. Full methodological
details are available in Online Supplemental Material A, but basic item
information, descriptives, and correlations are available in
\tblref{tab:??}.
